Interaction network structure maximizes community-level plant reproduction success via niche complementarity

### 2019-04-23 paper_round2.Rmd
slight change in intro

Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level. To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain. Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success. In addition, we evaluate whether community structure helps us explain differences in equity in reproductive success across individuals within a species and species within a community as a measure of evenness and stability in the pollination service.

>>>>

Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level. To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain. Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success. In addition, we evaluate whether community structure helps us explain differences in equity in reproductive success across species within a community as a measure of evenness and stability in the pollination service.
